Prefetching SPARQL query cacher

### 2016-08-03 dissertation/cache-proxy.tex
Make examples fit #18
Not even call it a cost model

The resulting plan trees may be represented as strings as follows:
\begin{example}{Four Attean plan trees}
\begin{verbatim}
- Hash Join { s } (distinct cost: 27)
-   Quad { ?s, <http://ex.org/p>, ?o, <g> } (cost: 15)
-   Quad { ?s, <http://ex.org/p>, "1", <g> } (cost: 12)

@@

- NestedLoop Join (distinct cost: 180)
-   Quad { ?s, <http://ex.org/p>, ?o, <g> } (cost: 15)
-   Quad { ?s, <http://ex.org/p>, "1", <g> } (cost: 12)
\end{verbatim}
\end{example}
In the above example, the first plan tree will be returned from the
query planner for execution, since it has the lowest estimated cost
(27). Since the SPARQL engine operates over quads, we have assigned a
dummy graph name when constructing the Model, namely
\rdfterm{<g>}.

The system we propose is based on this paradigm, any choices we make
are therefore to be encoded into a cost model. The cost model itself
is not considered a part of the contributions, it is a simple cost
model based on heuristics that arises from the following
discussion. The heuristics themselves are best considered an
implementation detail and is described in
Section~\ref{sec:costheuristics}.

>>>>

The resulting plan trees may be represented as strings as follows:
\begin{example}{Four Attean plan trees}
\small
\begin{verbatim}
- Hash Join { s } (distinct cost: 27)
-   Quad { ?s, <http://ex.org/p>, ?o, <g> } (cost: 15)
-   Quad { ?s, <http://ex.org/p>, "1", <g> } (cost: 12)

@@

- NestedLoop Join (distinct cost: 180)
-   Quad { ?s, <http://ex.org/p>, ?o, <g> } (cost: 15)
-   Quad { ?s, <http://ex.org/p>, "1", <g> } (cost: 12)
\end{verbatim}
\normalsize
\end{example}
In the above example, the first plan tree will be returned from the
query planner for execution, since it has the lowest estimated cost
(27). Since the SPARQL engine operates over quads, we have assigned a
dummy graph name when constructing the Model, in this case further
shortened to \rdfterm{<g>}.

The system we propose is based on this paradigm, any choices we make
are therefore to be encoded into a cost model. The cost model itself
is not considered a part of the contributions, as it is just
based on heuristics that arises from the following
discussion. The heuristics themselves are best considered an
implementation detail and is described in
Section~\ref{sec:costheuristics}.
